### 2010-12-16 doc/tech_doc/backend_interface/Backends-arc1.tex
Reorganizing doc catalogue and enabling make doc
Keep documentation up-to-date to the GLUE2 schema
Switching documents to bibliography style which is supposed to be present in latex distributions. Fixes in some documents and build procedures.
Update backends doc: GLUE2 is well supported now

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{graphicx}                              %for PNG images (pdflatex)
%\usepackage{graphics}                              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {T.Frågåt},
  pdftitle ={Arc batch system back-end interface guide with support for GLUE 2},
  pdfsubject = {Description and developer's guide for ARC1},
  pdfkeywords = {ARC,ARC1,NorduGrid,manual,Back-end,LRMS,Infosystem,GLUE2},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}                       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%

@@

The information system interface consists of a set of Perl scripts which
generates an XML output to \texttt{STDOUT} by one invocation of the Perl script named
\texttt{cluster+qju.pl}. The XML output includes two representations of the output data,
namely the classic NorduGrid information schema and an incomplete GLUE2 schema representation.

The information collector scripts are divided between several separate scripts:
\begin{itemize}
\item \texttt{cluster+qju.pl} - driver for information collection. It calls all other information collectors and prints the results in XML. The information collection is done by one single invocation of this script.
\item \texttt{InfoCollector.pm} - base class for all information collectors (i.e.: all files \texttt{*Info.pm}).
\item \texttt{InfoChecker.pm} - used by \texttt{InfoCollector} to validate options and results against a ``schema''.
\item \texttt{GMJobsInfo.pm} - collects information about jobs from GM status files.
\item \texttt{HostInfo.pm} - collects other information that can be collected on the front end (hostname, software version, disk space for users, installed certificates, Runtime environments, etc.)
\item \texttt{LRMSInfo.pm} - collects information that is LRMS specific (queues, jobs, local user limits, etc.) by calling the appropriate LRMS plugin. It also does validation of input options to the plugin and of the data returned by the plugin. 
\item \texttt{<BATCH\_SYSTEM\_NAME>.pm} - plugins for LRMSInfo. Only Fork, SGE and PBS are updated to the new framework.
\item \texttt{ARC0ClusterInfo.pm} - combines all information about A-REX and produces information structured according to the classic NorduGrid schema.
\item \texttt{ARC1ClusterInfo.pm} - combines all information about A-REX and produces information structured according to the GLUE2 schema.
\end{itemize}

@@

\section{The ARC GLUE2 implementation}
ARC1 provides support for both the classic NorduGrid information
schema~\cite{is} as well as an early minimal GLUE 2 implementation.
The output is rendered in XML format.

Currently, the the following GLUE2 entities are included in ARC1:
\begin{itemize}
\item ComputingService
\item ComputingEndpoint
\item ComputingShare
\end{itemize}

While the following entities are still missing:
\begin{itemize}
\item ApplicationEnvironment
\item ExecutionEnvironment
\item ComputingActivity
\item Policy including MappingPolicy / AccessPolicy
\end{itemize}

@@

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Value \\
\hline \hline
Capability & \texttt{executionmanagement.jobexecution} \\
\hline
Type & \texttt{org.nordugrid.arex} \\
\hline
QualityLevel & \texttt{development} \\
\hline
Complexity & \texttt{endpoint=1,share=N,resource=1}, where N is the number of queues in the configuration file\\
\hline
\end{tabular}

@@

\subsection{ExecutionEnvironment}
Not yet implemented.

\subsection{ApplicationEnvironment}
Not yet implemented.

\subsection{ComputingActivity}
Not yet implemented.

\subsection{MappingPolicy and AccessPolicy}
Not yet implemented.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{graphicx}                              %for PNG images (pdflatex)
%\usepackage{graphics}                              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {T.Frågåt},
  pdftitle ={Arc batch system back-end interface guide with support for GLUE2},
  pdfsubject = {Description and developer's guide for ARC1},
  pdfkeywords = {ARC,ARC1,NorduGrid,manual,Back-end,LRMS,Infosystem,GLUE2},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\usepackage[numbers]{natbib}
\bibliographystyle{plainnat}
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%

@@

The information system interface consists of a set of Perl scripts which
generates an XML output to \texttt{STDOUT} by one invocation of the Perl script named
\texttt{CEinfo.pl}. The XML output includes two representations of the output data,
namely the classic NorduGrid information schema and an incomplete GLUE2 schema representation.

The information collector scripts are divided between several separate scripts:
\begin{itemize}
\item \texttt{CEinfo.pl} - driver for information collection. It calls all other information collectors and prints the results in XML. The information collection is done by one single invocation of this script.
\item \texttt{InfoCollector.pm} - base class for all information collectors (i.e.: all files \texttt{*Info.pm}).
\item \texttt{InfoChecker.pm} - used by \texttt{InfoCollector} to validate options and results against a ``schema''.
\item \texttt{GMJobsInfo.pm} - collects information about jobs from GM status files.
\item \texttt{HostInfo.pm} - collects other information that can be collected on the front end (hostname, software version, disk space for users, installed certificates, Runtime environments, etc.)
\item \texttt{LRMSInfo.pm} - collects information that is LRMS specific (queues, jobs, local user limits, etc.) by calling the appropriate LRMS plugin. It also does validation of input options to the plugin and of the data returned by the plugin. 
\item \texttt{<BATCH\_SYSTEM\_NAME>.pm} - plugins for LRMSInfo. Only Fork, SGE and PBS are updated to the new framework.
\item \texttt{ARC0ClusterInfo.pm} - combines all information about A-REX and produces information structured according to the classic NorduGrid schema.
\item \texttt{ARC1ClusterInfo.pm} - combines all information about A-REX and produces information structured according to the GLUE2 schema.
\end{itemize}

@@

\section{The ARC GLUE2 implementation}
ARC1 provides support for both the classic NorduGrid information
schema~\cite{is} as well as GLUE2.
The output is rendered in XML format.

@@

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Value \\
\hline \hline
Capability & \texttt{executionmanagement.jobexecution} \\
\hline
Type & \texttt{org.nordugrid.execution.arex} \\
\hline
QualityLevel & \texttt{development} \\
\hline
Complexity & \texttt{endpoint=1,share=N,resource=1}, where N is the number of queues in the configuration file\\
\hline
\end{tabular}

@@

\subsection{ExecutionEnvironment}

\subsection{ApplicationEnvironment}

\subsection{ComputingActivity}

\subsection{MappingPolicy and AccessPolicy}
